canaper: Categorical analysis of neo- and paleo-endemism in R

### 2022-09-30 ms/ms.Qmd
Add set.seed()
Fix usage of seed in cpr_rand_test

```{r}
#| label: acacia-load
#| include: false
# Load pre-calculated results from targets pipeline
# - acacia_canape_cpr is Acacia CANAPE results calculated with canaper
# - rename it so we can use it in demo code below
acacia_canape <- tar_read(acacia_canape_cpr,
  store = here::here("_targets"))
```

@@

@@

# Load CANAPE results from canaper and biodiverse
tar_load(c(
  acacia_canape_cpr,
  acacia_canape_biod,
  acacia_canape_comp,
  acacia_biod_elapsed_min,
  # Enforce dependency on acacia_canape_cpr_1 for calculating times
  acacia_canape_cpr_1),
  store = here::here("_targets")
)

@@

# Make table comparing the two
comp_table <- left_join(
  count(acacia_canape_cpr, endem_type, name = "n_canaper"),
  count(acacia_canape_biod, endem_type, name = "n_biodiverse"),
  by = "endem_type")
```

@@

Computations were carried out on an MacBook Pro (2019) with 16 GB RAM and a 1.7 GHz, four core processor.
Approximate compute times were `r acacia_biod_elapsed_min` min for Biodiverse and `r times$acacia_canape_cpr_1$minutes` min for `canaper` (sequential, i.e., non-parallel mode, for both).
However, when parallel computing was enabled for `canaper` with two cores, compute time dropped to `r times$acacia_canape_cpr$minutes` min (further increases in number of cores did not significantly decrease time).
This demonstrates that `canaper` can efficiently compute moderately sized datasets with a personal laptop computer.

>>>>

```{r}
#| label: acacia-load
#| include: false
# Load pre-calculated results from targets pipeline
# - acacia_canape_cpr_1 is Acacia CANAPE results calculated with canaper
# - rename it so we can use it in demo code below
acacia_canape <- tar_read(acacia_canape_cpr_1,
  store = here::here("_targets"))
```

@@

# Set a seed for reproducibility
set.seed(12345)

@@

# Load CANAPE results from canaper and biodiverse
tar_load(c(
  acacia_canape_biod,
  acacia_canape_comp,
  acacia_biod_elapsed_min,
  acacia_canape_cpr_1,
  acacia_canape_cpr_2,
  acacia_canape_cpr_3),
  store = here::here("_targets")
)

@@

# Make table comparing the two
comp_table <- left_join(
  count(acacia_canape_cpr_1, endem_type, name = "n_canaper"),
  count(acacia_canape_biod, endem_type, name = "n_biodiverse"),
  by = "endem_type")
```

@@

Computations were carried out on an MacBook Pro (2019) with 16 GB RAM and a 1.7 GHz, four core processor.
Approximate compute times were `r acacia_biod_elapsed_min` min for Biodiverse and `r times$acacia_canape_cpr_1$minutes` min for `canaper` (sequential, i.e., non-parallel mode, for both).
However, when parallel computing was enabled for `canaper` with two cores, compute time dropped to `r times$acacia_canape_cpr_2$minutes` min (further increases in number of cores did not significantly decrease time).
This demonstrates that `canaper` can efficiently compute moderately sized datasets with a personal laptop computer.

### 2022-09-30 ms/si.Qmd
Fix usage of seed in cpr_rand_test

acacia_canape <-
  tar_read(
    acacia_canape_cpr,
    store = here::here("_targets")
  ) |>
  separate(site, c("long", "lat"), sep = ":") |>
  mutate(across(c(long, lat), parse_number))

>>>>

acacia_canape <-
  tar_read(
    acacia_canape_cpr_1,
    store = here::here("_targets")
  ) |>
  separate(site, c("long", "lat"), sep = ":") |>
  mutate(across(c(long, lat), parse_number))
